
\beginsong{Lemon Tree}[by={Fool s Garden}]
 \capo{8}
 \musicnote{Chords without * are played by picking the base note and then strumming down the other strings and doing the same again.}
 \gtab{F#dim7}{XX1212}
 \gtab{G}{320033}

 \ifchorded \beginverse*
  {\nolyrics \[Am] \[Em] \[Am] \[Em] \[Dm] \[Em] \[Am]  \[Em**]  \[Am*]}
 \endverse \fi

 \beginverse
  I'm \[Am]sitting here in a \[Em]boring room,
  It's \[Am]just another rainy Sunday \[Em]afternoon.
  I'm \[Am]wasting my time, I got \[Em]nothing to do.
  I'm \[Am]hanging around, I'm \[Em]waiting for you,
  But \[Dm]nothing ever \[Em]happens - and I \[Am]wonder. \[Am*] \[Em**]
 \endverse

 \beginverse
  I'm \[Am]driving around - \[Em]in my car,
  I'm \[Am]driving too fast, I'm \[Em]driving too far.
  I'd \[Am]like to change my \[Em]point of view
  I \[Am]feel so lonely, I'm \[Em]waiting for you
  But \[Dm]nothing ever \[Em]happens - and I \[Am]wonder. \[Am*] \[Em**]
 \endverse

 \beginchorus
  I \[C]wonder how, I \[G]wonder why
  \[Am]Yesterday you told me 'bout the \[Em]blue blue sky
  And \[F]all that I can \[G]see is just a yellow \[C]lemon tree. \[G7]
  I'm \[C]turning my head - \[G]up and down,
  I'm \[Am]turning turning turning turning \[Em]turning around
  And \[F]all that I can \[F#dim7]see is just another \[G]lemon tree. \[G7]
 \endchorus

 \beginverse
  \[Am]Dam \[Am]    \[Em]dado\[Em]udi.\[Am]... \[Am*] \[Em**] \[Am] \[Em] \[Em] \[Dm] \[Dm] \[Em] \[Em] \[Am]
 \endverse

 \beginverse
  I'm \[Am]sitting here, I \[Em]miss the power.
  I'd \[Am]like to go out, tak\[Em]ing a shower,
  But \[Am]there's a heavy cloud \[Em]inside my head.
  I \[Am]feel so tired, put my\[Em]self into bed,
  Where \[Dm]nothing ever \[Em]happens - and I \[Am]wonder. \[Am*] \[Em**]
 \endverse

 \beginverse
  \[E]Isolation - \[Am]Is not good for me,
  \[G]Isolation - \[C]I don't want to \[E]sit on a lemon tree.
 \endverse

 \beginverse
  I'm \[Am]stepping around in a \[Em]desert of joy
  \[Am]Baby, anyhow I'll get \[Em]another toy
  And \[Dm]everything will \[Em]happen - and you \[Am]wonder. \[Am*] \[Em**]
 \endverse

 \beginchorus
  I \[C]wonder how, I \[G]wonder why
  \[Am]Yesterday you told me 'bout the \[Em]blue blue sky
  And \[F]all that I can \[G]see is just another \[C]lemon tree. \[G7]
  I'm \[C]turning my head - \[G]up and down,
  I'm \[Am]turning turning turning turning \[Em]turning around
  And \[F]all that I can \[F#dim7]see is just the yellow \[G]lemon tree. \[G7]
 \endchorus

 \ifchorded \beginverse*
  I \[C]wonder how, I \[G]wonder why
  \[Am]Yesterday you told me 'bout the \[Em]blue blue sky
  And \[F]all that I can \[G]see, and \[F]all that I can \[G]see,
  And \[F]all that I can \[G]see is just a yellow \[C]lemon tree.
 \endverse \fi
\endsong