
\beginsong{Angel Of Small Death And The Codeine Scene}[by={Hozier}]
 \capo{2}

 \ifchorded \beginverse*
  {\nolyrics \[Em]    \[B7]  \[Em]  \rep{2}}
 \endverse \fi

 \beginverse
  \[Em]I watch the work of my \[B7]kin, bold and \[Em]boyful
  \[Em]Toying somewhere between \[B7]love and a\[Em]buse
  \[D]Calling to join them, the \[G]wretched and joyful
  \[Em]Shaking the wings of their \[B7]terrible y\[Em]ouths
 \endverse

 \beginverse
  \[Em]Freshly disowned in some f\[B7]rozen dev\[Em]otion
  \[Em]No more alone or mys\[B7]elf could I \[Em]be.
  \[D]Lurched like a stray to the \[G]arms that were open,
  No \[Em]shortage of sordid, no \[B7]protest from \[Em]me.
 \endverse

 \beginchorus
  With her\[Em] sweetened breath, and her\[G] tongue so mean
  She's the\[D] angel of small death and the\[Em] codeine scene.
  With her\[Em] straw-blonde hair, her arms\[G] hard and lean,
  She's the\[D] angel of small death and the\[Em] codeine scene.
 \endchorus

 \beginverse
  \[Em]Feeling more human and \[B7]hooked on her f\[Em]lesh,
  I \[Em]lay my heart down with the \[B7]rest at her \[Em]feet.
  \[D]Fresh from the fields, all \[G]fetor and fertile,
  \[Em]Bloody and raw, but I \[B7]swear it is \[Em]sweet.
 \endverse

 \repeatchorus

 \beginverse
  \[Em]Oh   \[Bm]Ooh  \[G]Oooh  \[Am]Oh   \[C]Ooooo\[D]hoho\[G]h\[G]
 \endverse

 \ifchorded \beginverse*
  {\nolyrics \[Am]   \[Em]   \[Bm]    \[C]    \[C]    \[G]}
 \endverse \fi

 \beginverse
  In \[Em]leash-less confusion, I'll \[B7]wander the \[Em]concrete,
  \[Em]Wonder if better now \[B7]having sur\[Em]vived.
  \[D]Jarring of judgement and \[G]reasons defeat,
  The sweet \[Em]heat of her breath in my \[B7]mouth, I'm a\[Em]live.
 \endverse

 \repeatchorus \rep{2}
\endsong
