
\beginsong{Lions}[by={Dire Straits}]
 \capo{2}
 \gtab{Bb9}{X13111}
 \gtab{Dm9}{XX0210}

 \ifchorded \beginverse*
  {\nolyrics | \[Am7] | \[C] | \[G] | \[F7] |}
  {\nolyrics | \[Am7] | \[Am7] | \[Am7] | \[Em7] \[Bb9]   |}
 \endverse \fi

 \beginverse
  \[Am7]Red sun,\[C] goin' down,\[G] way over\[F7] dirty town.
  \[Am7]  Starlings, they're \[C]sweepin' around them\[G] crazy sho\[D7]als.
  \[Am7]  Yes, and  a gi\[C]rl is there,\[G] high  heelin' out a\[F7]cross the square.
  \[Am7]  Wind it blows a\[C]round in her hair \[G] and the flags upon the \[D7]poles.
  \[Dm9] Waitin' in the crowd to cross at the light,\[Dm9] she looks around
  to \[Fdim]find a fa\[E7]ce she can\[|] l\[Am7]ike.\[|]  \[Em7]    \[|]Uh\[Am7] huh\[|].\[Em7] \[Bb9] \[|]
 \endverse

 \beginverse
  \[Am7]Church bell\[C] clingin' on, just a t\[G]ryin' to get a crowd\[F7] for eve'n song.
  \[Am7] Nobody cares to de\[C]pend upon\[G] the chime it \[D7]plays.
  \[Am7]They're all in the station \[C]prayin' for trains.\[G] The congragation\[F7] late again.
  \[Am7] It's gettin' darker\[C] all the time these \[G]flagpole \[D7]days.
  \[Dm9]Drunk old soldier, he give her a fright.
  He's a \[Dm9]crazy liion, he's a \[Fdim]howlin'\[E7] for a\[|] f\[Am7]ight\[|]. \[Em7]   U\[|]h \[Am7]huh.\[|] \[Em7] \[Bb9] \[|]
 \endverse

 \ifchorded \beginverse*
  {\nolyrics | \[Am7] | \[C] | \[G] | \[F7] | \rep{2}}
  {\nolyrics | \[Am7] | \[Am7] | \[Am7] | \[Em7] \[Bb9]  |}
 \endverse \fi

 \beginverse
  \[Am7]Strap hangin',\[C] gunshot sound,\[G] doors slaming on the\[F7] overground.
  \[Am7] The starlings are tough\[C], but the \[G]lions are made of s\[D7]tone.
  \[Am7]Her evening paper is\[C] horror torn, but there's \[G]hope for later,\[F7] Capricorn.
  \[Am7] Lucky stars give her \[C]just enough\[G] to get her \[D7]home.
  \[Dm9] Then she'll read about a swing to the right,
  \[Dm9]But she's athinkin' 'bout a s\[Fdim]tranger\[E7] in the \[Am7]night\[Em7].
 \endverse

 \beginchorus
  \[F]  I'm thinkin' 'bout the \[G]lions.
  \[F]   Thinkin'  'bout the \[G]lions.
  \[F]  What happened to the \[Gsus4]lions to\[Am7]night\[Em7]?
                                   (night)
  To\[Am7]night\[Em7],  t\[Am7]onigh\[Em7]t, u\[Am7]h hu\[G]h
 \endchorus

 \ifchorded \beginverse*
  \[G]   Thinking about the lions
 \endverse \fi
\endsong